Supplementary Materials

### 2023-07-03 manuscript/supplementary.tex
minor ms changes

\subsection{Additional Residual Diagnostics}

@@

\begin{figure}[htbp]
  \label{suppfig:dfe-ceu}
  \centering
  \includegraphics[width=0.6\textwidth]{figures/supplementary/figure_ceu_dfe.pdf}
  \caption{The DFE across models for the CEU reference sample (analogous to the
  DFE for YRI samples in Figure \ref{fig:figure-3}.}
\end{figure}

\begin{figure}[htbp]
    \label{suppfig:dfe-chb}
  \centering
  \includegraphics[width=0.6\textwidth]{figures/supplementary/figure_chb_dfe.pdf}
  \caption{The DFE across models for the CHB reference sample (analogous to the
  DFE for YRI samples in Figure \ref{fig:figure-3}.}
\end{figure}

>>>>

\subsection{Demographic Expansion and Recessive Simulation Tests}

\begin{figure}[htbp]
    \label{suppfig:sim-exp}
  \centering
  \includegraphics[width=0.8\textwidth]{figures/supplementary/subfigure_sim_mle_expansion.pdf}
  \caption{}
\end{figure}

\begin{figure}[htbp]
  \label{suppfig:sim-rec}
  \centering
  \includegraphics[width=0.8\textwidth]{figures/supplementary/subfigure_sim_mle_recessive.pdf}
  \caption{}
\end{figure}

\subsection{Residual Covariate Diagnostics}

@@

\begin{figure}[htbp]
  \label{suppfig:dfe-ceu}
  \centering
  \includegraphics[width=0.9\textwidth]{figures/supplementary/figure_ceu_dfe.pdf}
  \caption{The DFE across models for the CEU reference sample (analogous to the
  DFE for YRI samples in Figure \ref{fig:figure-3}.}
\end{figure}

\begin{figure}[htbp]
    \label{suppfig:dfe-chb}
  \centering
  \includegraphics[width=0.9\textwidth]{figures/supplementary/figure_chb_dfe.pdf}
  \caption{The DFE across models for the CHB reference sample (analogous to the
  DFE for YRI samples in Figure \ref{fig:figure-3}.}
\end{figure}
